---
title: "Demean_63"
author: "Thania Balducci"
date: "28/7/2020"
output: 
  html_document:
    toc: true
    code_folding: show
    toc_float: 
        collapsed: false
        smooth_scroll: true
    number_sections: true
---

```{r setup, message=F, echo=F}
# some custom options to generate a nice html file
options(digits = 3)
options(width=100)


packages <- c("lsr","coin","car", "stats")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())), repos='http://cran.us.r-project.org')  
}

library("car")
library("lsr")
library("data.table")
library("lfe")
library("Jmisc")


library(knitr)
opts_chunk$set(cache=F, comment='#', tidy = T, tidy.opts=list(blank=T, width.cutoff=100), fig.align='center', message=F, warning=T, fig.width=6, fig.height=6, dev='svg',eval=T)
```

#Importing the data

```{r}
DMdemo_63 <- readRDS("C:/Users/baldu/Documents/demo_63.rds")

Cl_DMdemo_63 <- DMdemo_63

Cl_DMdemo_63_fm <- droplevels(Cl_DMdemo_63[Cl_DMdemo_63$gp == 0,])
Cl_DMdemo_63_hc <- droplevels(Cl_DMdemo_63[Cl_DMdemo_63$gp == 1,])
```

#Visualize outliers

```{r}

#age
boxplot(Cl_DMdemo_63$X1_age ~ Cl_DMdemo_63_fm$gp)

#education
boxplot(Cl_DMdemo_63$X1_yr_study ~ Cl_DMdemo_63_fm$gp)
```

#Extract outliers

```{r}

#education
OL_DMyr_study_63_fm <- boxplot(Cl_DMdemo_63_fm$X1_yr_study ~ Cl_DMdemo_63_fm$gp, plot = FALSE)$out
OL_DMyr_study_63_hc <- boxplot(Cl_DMdemo_63_hc$X1_yr_study ~ Cl_DMdemo_63_hc$gp, plot = FALSE)$out

#tas - eos
(OL_taseot_63 <- boxplot(Cl_tas_63$X11_eot, plot = FALSE)$out) #TAS eot: 38, 39, 37
(which(Cl_tas_63$X11_eot == 38)) #index 3
(which(Cl_tas_63$X11_eot == 39)) #index 7
(which(Cl_tas_63$X11_eot == 37)) #index 13
Cl_tas_63$ï..rid[c(3,7,13)] #rid
```

#Identify outliers

```{r}

#education
Cl_DMdemo_63_hc$X1_yr_study[Cl_DMdemo_63_hc$X1_yr_study %in% OL_DMyr_study_63_hc] <- NA

Cl_tas_63$X11_eot[Cl_tas_63$X11_eot %in% OL_taseot_63] <- NA
```

#Demean by group

```{r}

#age
DMage_63_fm <- demeanlist(Cl_DMdemo_63_fm$X1_age, list(Cl_DMdemo_63_hc$gp), na.rm = TRUE)
DMage_63_hc <- demeanlist(Cl_DMdemo_63_hc$X1_age, list(Cl_DMdemo_63_hc$gp), na.rm = TRUE)

#education
DMyr_study_63_fm <- demeanlist(Cl_DMdemo_63_fm$X1_yr_study, list(Cl_DMdemo_63_hc$gp), na.rm = TRUE)

DMyr_study_63_hc <- demeanlist(Cl_DMdemo_63_hc$X1_yr_study, list(Cl_DMdemo_63_hc$gp), na.rm = TRUE)
DMyr_studyNA_63_hc <- c(NA,NA,DMage_63[1:21], NA, DMage_63[22:28]) #Add outliers (index 1,2,24)

```

#Demean all (one group) ordered by rid

                           demeaned
age             x              done
education       yes            done 
yrs dx          yes
yrs symptoms    yes
no daily med    x
fiq             yes
wpi             x              done
sss             x              done
tender points   x              done
hamd_total      x              done
hamd_III        x              done
hama_total      x              done
ERQ-S           x              done
ERQ-R           x              done
TAS-ID feelings x              done
TAS-describing  x              done
TAS-external    yes            done
TAS total       yes            done
PANAS-p-lw      yes            done
PANAS-p-g       x              done
PANAS-n-lw      x              done
PANAS-n-g       x              done
McGill-a        x
McGill-ts       x
ipo-id diffusionx              done    
ipo-childish    yes            done
ipo-paranoid    x              done
ipo-pathologicORx              done
perf_o          yes
perf_i          yes
perf_d          yes
perf_s          yes
perf_mean       x              done

When multiple groups of subjects are involved, centering becomes more complicated. Sometimes overall centering makes sense. However, in contrast to the popular misconception in the field, under some circumstances within-group centering can be meaningful (and even crucial) and may avoid the following problems with overall or grand-mean centering:
loss of the integrity of group comparisons;
multi-collinearity;
invalid extrapolation of linearity.

https://sscc.nimh.nih.gov/pub/dist/doc/htmldoc/STATISTICS/center.html

```{r}

#age 

DMage63_all_fm <- demeanlist(Cl_demo_63$X1_age, na.rm = TRUE)

#education
DMyr_study_63 <- demeanlist(Cl_demo_63$X1_yr_study, list(Cl_demo_63$DMfx), na.rm = TRUE)
DMyr_studyNA_63 <- c(NA, DMyr_study_63[1:2], NA, DMyr_study_63[3:7], NA, DMyr_study_63[8:52], NA, DMyr_study_63[53:59]) #Add outliers (index 1,4,10,56)



#wpi
DMwpi_63 <- demean(Cl_ara10_63$X3_wpi_sc)

#sss
DMsss_63 <- demean(Cl_ara10_63$X3_sss_ts)

#tender points
DMtp_63 <- demean(Cl_ara90_63$X4_tc)

#hamd_total 
DMhamd_t_63 <- demean(Cl_ham_63$X6_hamd_total)

#hamd_III       
DMhamd_III_63 <- demean(Cl_ham_63$X6_hamd_III)

#hama_total    
DMhama_63 <- demean(Cl_ham_63$X7_hama_total)

#ERQ-S    
DMerq_s_63 <- demean((Cl_erq_63$X10_S))

#ERQ-R          
DMerq_r_63 <- demean((Cl_erq_63$X10_R))

#TAS-ID feelings 
DMtas_ID_63 <- demean(Cl_tas_63$X11_id)

#TAS-describing  
DMtas_df_63 <- demean(Cl_tas_63$X11_df)

#TAS-external
DMtas_eot_63 <- demeanlist(as.numeric(Cl_tas_63$X11_eot), list(Cl_demo_63$DMfx), na.rm = TRUE)
DMtas_eotNA_63 <- c(DMtas_eot_63[1:2], NA, DMtas_eot_63[3:5], NA, DMtas_eot_63[6:10], NA, DMtas_eot_63[11:60]) #Add outliers (index 3,7,13)

#tas total
DMtas_ts_63 <- demeanlist((Cl_tas_63$X11_ts), list(Cl_demo_63$DMfx), na.rm = TRUE)
DMtas_tsNA_63 <- c(NA, DMtas_ts_63[1:5], NA, DMtas_ts_63[6:10], NA, DMtas_ts_63[11:60]) #Add outliers (index 1,7,13)

#panas - positive last week
DMpanas_plw_63 <- demeanlist((Cl_panas_63$X13_p_lw), list(Cl_demo_63$DMfx), na.rm = TRUE)

#panas - positive general
DMpanas_pg_63 <- demean(Cl_panas_63$X13_p_g)

#panas - negative last week
DMpanas_nlw_63 <- demean(Cl_panas_63$X13_n_lw)

#panas - negative general
DMpanas_ng_63 <- demean(Cl_panas_63$X13_n_g)

#ipo - identity difussion
DMipo_id_63 <- demean(Cl_ipo_63$X9_ID_PC)

#ipo - childish
DMipo_ori_63 <- demeanlist((Cl_ipo_63$X9_ORI_PC), list(Cl_demo_63$DMfx), na.rm = TRUE)
DMipo_oriNA_63 <- c(DMipo_ori_63[1:4],NA,DMipo_ori_63[5:62]) #Add outliers (index 5)

#ipo - paranoid
DMipo_ORP_63 <- demean(Cl_ipo_63$X9_ORP_PC)

#ipo - pathologic object relationships
DMipo_ORP_63 <- demean(Cl_ipo_63$X9_POR_PC)

#task perf mean
DMtask_perfmean_63 <- demean(Cl_task_63$p_mean)
```