---
title: "Emotion intensity - HAMA"
author: "Thania Balducci"

html_document:
    toc: true
    code_folding: show
    toc_float: 
        collapsed: false
        smooth_scroll: true
    number_sections: true
---
```{r setup, message=F, echo=F}
# some custom options to generate a nice html file
options(digits = 3)
options(width=100)

library("car")
library("rcompanion")
library("mosaic")
library("visreg")
library("multcomp")
library("pls")
library("ridge")
library("glmnet")
library("ggplot2")
library("ppcor")

library("knitr")
opts_chunk$set(cache=F, comment='#', tidy = T, tidy.opts=list(blank=T, width.cutoff=100), fig.align='center', message=F, warning=T, fig.width=6, fig.height=6, dev='svg',eval=T)
```

# Importing the data
```{r}
arxhama <- read.csv("G:/bases/neg_vas_ar.csv")

arxhama[4:5] <- lapply(arxhama[4:5], as.numeric)

arxhama_fm <- droplevels(arxhama[arxhama$gp == 0,])
arxhama_hc <- droplevels(arxhama[arxhama$gp == 1,])

str(arxhama)
```

# Exploring all
```{r}
#visualization
boxplot(arxhama$X7_hama_total) #no OL
boxplot(arxhama$vas_ar) #OL 3

#homoscedasticity
leveneTest(arxhama$X7_hama_total ~ as.factor(gp), data = arxhama) #not same
leveneTest(arxhama$vas_ar ~ as.factor(gp), data = arxhama) #same

#Normality
shapiro.test(arxhama$X7_hama_total) #not normal
shapiro.test(arxhama$vas_ar) #normal

#transform HAMA
plotNormalHistogram(arxhama$X7_hama_total)
arxhama$t_hama_total <- transformTukey(arxhama$X7_hama_total)
plotNormalHistogram(arxhama$t_hama_total)

#transform HAMD
plotNormalHistogram(arxhama$X6_hamd_total)
arxhama$t_hamd_total <- transformTukey(arxhama$X6_hamd_total)
plotNormalHistogram(arxhama$t_hama_total)
```

# correlation all (w OL)
```{r }
scatterplot(arxhama$X7_hama_total, arxhama$vas_ar)
cor.test(arxhama$t_hama_total, arxhama$vas_ar, method = "spearman")
```
cor 
0.27
p-value = 0.03

# remove OL
```{r }
(OL_vas_ar <- boxplot(arxhama$vas_ar, plot = FALSE)$out) # 0.89  9.00 8.56
(which(arxhama$vas_ar <=0.89)) #index 4
(which(arxhama$vas_ar >=8.56)) #index 40 57
arxhama$rid[c(4,40,57)] # rid 8 52 73

#HAMA OL: none
#vas_int outliers: rid 8 52 73 (index 4, 40, 57)
arxhama.woOL <- arxhama[-c(4, 40, 57),]
```

# correlation all (wo OL)
```{r }
scatterplot(arxhama.woOL$t_hama_total, arxhama.woOL$vas_ar)
cor.test(arxhama.woOL$t_hama_total, arxhama.woOL$vas_ar, method = "spearman")
```

# correlation all for depression (wo OL)
```{r }
scatterplot(arxhama.woOL$t_hamd_total, arxhama.woOL$vas_ar)
cor.test(arxhama.woOL$t_hamd_total, arxhama.woOL$vas_ar, method = "spearman")
```

# Exploring FM depression for depression
```{r}
#visualization
boxplot(arxhama_fm$X6_hamd_total) #no OL
boxplot(arxhama_fm$vas_ar) #2 OL

#Normality
shapiro.test(arxhama_fm$X6_hamd_total) #normal
shapiro.test(arxhama_fm$vas_ar) #not normal

#transform arousal
plotNormalHistogram(arxhama_fm$vas_ar)
arxhama_fm$t_vas_ar <- transformTukey(arxhama_fm$vas_ar)
plotNormalHistogram(arxhama_fm$vas_ar)

#visualization
boxplot(arxhama_fm$t_vas_ar) #2 OL
```
# remove OL
```{r }
(OLfm_vas_ar <- boxplot(arxhama_fm$t_vas_ar, plot = FALSE)$out) # 0.79 85.57
(which(arxhama_fm$t_vas_ar <=0.79)) #index 3
(which(arxhama_fm$t_vas_ar >=85.57)) #index 25
arxhama_fm$rid[c(3,25)] # rid 8 52

#HAMA OL: none
#vas_ar outliers: rid 8 52 (index 3, 25)
arxhama_fm.woOL <- arxhama_fm[-c(3, 25),]
```

# correlation fm depression
```{r }
scatterplot(arxhama_fm.woOL$X6_hamd_total, arxhama_fm.woOL$t_vas_ar)
cor.test(arxhama_fm.woOL$X6_hamd_total, arxhama_fm.woOL$t_vas_ar, method = "spearman")
```
cor 
-0.005 
p-value = 1

# Exploring FM depression for anxiety
```{r}
#visualization
boxplot(arxhama_fm$X7_hama_total) #no OL
boxplot(arxhama_fm$vas_ar) #2 OL

#Normality
shapiro.test(arxhama_fm$X7_hama_total) #normal
shapiro.test(arxhama_fm$vas_ar) #not normal

#Use arxhama_fm$t_vas_ar for arousal column in the arxhama_fm.woOL df
```

# correlation fm anxiety
```{r }
scatterplot(arxhama_fm.woOL$X7_hama_total, arxhama_fm.woOL$t_vas_ar)
cor.test(arxhama_fm.woOL$X7_hama_total, arxhama_fm.woOL$t_vas_ar, method = "spearman")
```
# Exploring HC
#```{r}
#visualization
boxplot(intxhamd_hc$X6_hamd_total) #3 OL
boxplot(intxhamd_hc$vas_int) #1 OL

(OL_vas_int_hc <- boxplot(intxhamd_hc$X6_hamd_total, plot = FALSE)$out) # 5 7 4 5 5
(OL_vas_int_hc <- boxplot(intxhamd_hc$vas_int, plot = FALSE)$out) # 10.00
(which(intxhamd_hc$X6_hamd_total >=4)) #index 5 9 14 22 31
(which(intxhamd_hc$vas_int >=9.99)) #index 19
intxhamd$rid[c(5,9,14,22,31)] # rid 10 15 20 29 40
intxhamd$rid[c(19)] # rid 25

#HAMD OL: rid 10 15 20 29 40 (index 5,9,14,22,31)
#vas_int outliers: rid 25 (index 19)
intxhamd_hc.woOL <- intxhamd_hc[-c(5,9,14,19,22,31),]
```

# correlation hc
#```{r }
scatterplot(intxhamd_hc.woOL$X6_hamd_total, intxhamd_hc.woOL$vas_int)
cor.test(intxhamd_hc.woOL$X6_hamd_total, intxhamd_hc.woOL$vas_int, method = "spearman")
```

For HC wo
-0.116
p-value = 0.5


#correlation int and wpi controled by HAMD

#```{r }
cor.test(intxhamd$vas_int, intxhamd$wpi, method = "spearman")
pcor.test(intxhamd$vas_int, intxhamd$wpi, intxhamd$X6_hamd_total, method = "spearman")
```

Corr -0.461 p-value = 2e-04

pcor
estimate p.value 
  -0.184    0.16 
  
  
#Control of arousal per depression
In task_vas_61